Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches

### 2021-04-05 paper.tex
progress

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        \kktodo{uzerinden 
        gecelim}\\
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $\Gamma_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its outgoing edges\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
        \hline\hline
        $w_{u,v}$             & Sampling probability for the edge $(u,v)$\\
        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal Gain after last sketch build\\
        $Err_l$         & Local estimation error of the sketch\\
        $Err_g$         & Global estimation error of the sketch\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c}$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

\begin{figure}[!ht] 
    \centering
  \subfloat[\small{IC}\label{fig:ic}]{%
       \includegraphics[width=0.37\linewidth]{images/ic.pdf}}
  \subfloat[\small{WC}\label{fig:wc}]{%
        \includegraphics[width=0.37\linewidth]{images/wc.pdf}}
    \\% IMAGES HERE
  \caption{\protect\subref{fig:ic} 
\kktodo{a parti nonuniform weight olsun} The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
\protect\subref{fig:wc}
The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?} 
  }
  %\label{fig_ic_model} 
  \label{fig:xx} 
\end{figure}

@@

\item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set the edge weights as shown in Figure~\ref{fig:wc}.
The method, as described in~\cite{kempe2003maximizing}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
of incoming edges of $v$~(which in the original graph is equal to $\Gamma _G(v)$).
Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var } Note that the model is originally defined for undirected graphs in~\cite{MixGreedy}. However, the definition above is consistent since one can consider each~(undirected) edge as two directed edges.

@@

The reachability set of a vertex is the union of those of all its connected vertices (via outgoing edges). Many IM kernels exploit this property to some degree. The methods based on {\em reverse reachability} \kktodo{cite} and {\em bottom-up traversal} \kktodo{cite} utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced. {\em MixGreedy} \kktodo{cite} goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set. Therefore, all the reachability sets within a single sample subgraph can be found via a single graph traversal.

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
If one-hot vectors are used to store the reachability sets for constant insertion time $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity. 
If disjoints sets are used for storing reachability sets; $\mathcal{O}(n\bar{\sigma}\mathcal{R})$ \kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann function \kktodo{bu Ackermann'a atif verelim}.

@@

In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average length of the longest leading zeros. Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed, by taking the pairwise maximums of their registers. Formally; 
\begin{equation}
\label{eq:sketch-merge}
    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq J.
\end{equation} 
In our implementation, the merge operations are performed if and only if there is an edge between the vertices in respective samples \kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}. \ggx{ j'th sampleda vertexler arasında sampled edge olmasını kastetmiştim. Yanlis olmus.}

@@

Most IM algorithms have the same few steps to find the best seed vertex set; sampling, building the influence oracle, verifying the impact of new candidates, then removing the residual reachability set of the latent seed set. Following the idea proposed in~\cite{infuser}, \acro fuses the sampling step with other steps to avoid reading the graph multiple times.

@@

Throughout the process, each register is used only for a single sample/simulation. A merge operation for an edge ($u, v$) of the graph is performed on $v$'s register if and only if the edge exists in the sample and \kktodo{bunu da degistirdim} $u$ is {\em live} in the current iteration. This process iteratively relays the reachability information among the vertices. At each iteration, the sketches of the current reachable vertices are modified. \kktodo{onceki cumleyi de degistirdim - dogru mu} 
Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, and/or path-by-path, all the influence that passes through the edges in a single step is processed together. 
This recursive formulation of the influence allows us to estimate the marginal influence for all vertices very fast. 
After the computation of reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches. Then \acro calculates the reachability set of the latent seed set, i.e., the one that contains the current set and $v$, by performing Monte-Carlo simulations. The vertices in the reachability sets are labeled {\em blocked} \kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekildeydi} in the respective samples. Finally, the algorithm checks if a rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate. \kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.

\subsection{Hash-based Fused Sampling}
The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process. If performed individually as a preprocessing step, as the literature traditionally does, the sampling stage can be an expensive, furthermore, a time-wise dominating one for the overall IM kernel; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large, and second, if samples are memoized, the memory requirement can be a multiple of the graph size. 
In this work, we borrow the fused sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of in-memory creation and storage of the sample subgraphs.\kktodo{burata alttaki figure atfen basitce ne oldugunu anlatan 2-3 cumle gerek}

@@

\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{./images/bias.pdf}
    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks. \kktodo{bias matematiksel olarak nasil hesaplanir. bunu buraya yazalim}}
    \label{fig:prob-bias} 
\end{figure}

% For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
% Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. 
%Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
Being able to generate the samples on-the-fly allows us to avoid many memory accesses. The only downside of hash-based fused sampling is that we have to generate all these random values,   $P(u,v)_r$, for each edge traversal and each simulation $r$. To reduce this cost and leverage the performance gains of fused sampling better, the edges' hash values are precomputed for all the edges in $E$. Fortunately, the rest of the operations, i.e., one XOR and one division, are quite fast on modern computing hardware. %The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.

@@

\begin{algorithm}
\caption{\sc{\acro}($G,K,J$)}
\label{algo:main}
\algorithmicrequire{$G = (V,E)$: the influence graph
\\\hspace*{6.6ex}{$K$: number of seed vertices
\\\hspace*{6.7ex}$J$: number of MC simulations}\\}
\algorithmicensure{$S$: a seed set that maximizes influence on $G$
}
\begin{algorithmic}[1]
    \State {$S \leftarrow \{\emptyset\}$}
    \For{$ v\in V$} {\bf in parallel}
        \For{$ j\in J$}
            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
        \EndFor
    \EndFor
    \State $M \leftarrow ${\sc Simulate}$(G,M,\emptyset)$
    \State $M_{S'} \leftarrow zeros(J)$
    \State $\varsigma \leftarrow 0$
    \For{$k=1\ldots K$}
        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}}\{${\sc Estimate}$(${\sc Merge}$(M_{S'},M_v))$\}\kktodo{S' nedir}
        \State $S \leftarrow S \cup \{s\}$
        \State $e \leftarrow ${\sc Estimate}$(${\sc Merge}$(M_{S'},M_s))$
        % \State $R_S \leftarrow run\_cascade(G,S,J)$
        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ \kktodo{buna da bir algoritma eklesek} }
        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
        \State $\delta = \sigma - \varsigma$
        \State $Err_l=|(e - \delta) / \delta|$
        \State $Err_g=|e-\delta| / \sigma $
        \If{$ Err_l < \epsilon_l \lor Err_g < \epsilon_g$} %FIXME
            \State $M_{S'} \leftarrow merge(M_{S'},M_s)$
        \Else
            \For{$ v\in V$} {\bf in parallel}
                \For{$ j\in J$}
                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
                \EndFor
            \EndFor
            \State $M \leftarrow ${\sc Simulate}$(G,M,R_S)$
            \State $M_{S'} \leftarrow zeros(J) $ 
            \State $\varsigma \leftarrow \sigma $ 
        \EndIf
    \EndFor
    \State \Return $S$
\end{algorithmic}
\end{algorithm}

 Algorithm~\ref{algo:main} first initializes the reachability sets of all vertices by adding the vertices themselves. That is for all vertices $u$, its $j$th register is set to $M_u[j]=clz(h_j(u))$ meaning $R_{{G}_j}(u) = \{u\}$ where $G_j$ is the $j$th sampled graph. Then, we perform the diffusion process on the sketch registers. To initiate the process, all the vertices are added to the {\em live vertex set} $L$. Then the incoming edges of the live vertices are processed. If a vertex $u$ is live, its outgoing edges $(u, v)$ s.t. $v \in \Gamma_G(v)$ are processed and the sketches of $v$ are merged into those of $u$. \kktodo{burada edgeleri tersten process ettigimizi aciklamamiz gerek} If any of $u$'s sketch registers change, it is added to the live vertex set $L'$ of the next iteration. After the incoming edges of all live vertices are processed, the current iteration ends. If the cardinality of the next iteration's live vertex set, $|L'|$, is smaller than the convergence threshold $\epsilon_c$, the diffusion stops. Otherwise, $L$ is set to $L'$, and $L'$ is cleared. Then, the next iteration starts. Figure~\ref{fig:hf-processing} performs two simulations\kktodo{ bunu tamamlayalim}

\begin{figure*}[!ht]
    \begin{center}
    \includegraphics[width=0.7\linewidth]{images/sketch-diffusion.pdf}
    \caption{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green) and their registers are initialized with the length of the zero prefix of their hashes. (b) 
    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
    For the live edge between Vertex 1 and 4, \kktodo{bu edge nedir - outgoing luyor?} the register is set to the maximum of the respective register. Since the first register of vertex 1 has a larger value, we only update the second register. Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register. Notice that we are moving registers in reverse, from target to source of the edges. We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.  (d) All vertices have registers converged. There are no live vertices. }\label{fig:hf-processing} 
    \end{center}
    \end{figure*}

@@

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.8\linewidth]{images/sketch-saturation.pdf}
    \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding. \kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel}
     }\label{fig:sketch-saturation} 
    \end{center}
\end{figure}

@@

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The estimation error is calculated as the following; we store influence score after each sketch rebuild on $\varsigma$ and sketch cardinality estimate of the candidate vertex on $e$. We calculate the marginal gain after the last sketch build, $\delta=\varsigma - \sigma$. Then, the local estimation error will be $Err_l=|e-\delta / \delta|$ \kktodo{deltayi deltaya niye boluyoruz, ne cikmasini bekliyoruz} and global error rate $Err_g=|e-\delta / \sigma|$. 
The sketches are assumed as stale if the absolute error in the estimated total influence score, $Err_g$, is more than the global threshold, $\epsilon_{g}$, 
and the marginal gain estimation error, $Err_l$, after the last sketch is larger than a local threshold $\epsilon_{l}$.

Before rebuilding stale sketches, the reachability set of the latent seed set, $R_G(S')$, is marked as visited and considered blocked in their respective simulations while rebuilding the sketches. Then, the sketches are rebuilt using Monte-Carlo simulations. After rebuilding, $M_S$, which holds the cardinality estimate of the seed vertices added after the last rebuild, is cleared with all zeros.

The use of two threshold values allows the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
If a rebuild is not required, we only update $M_S$ by merging it with the candidate vertex's sketch. 
This approach allows us to keep the sketches in high quality even after many vertices are added to the seed set. But on the other hand, it forces us to perform expensive Monte-Carlo simulations. 
We reuse the reachability sets of the latent seed set, $R_G(S')$, computed by Monte-Carlo simulations. While rebuilding the sketches, $R_G(S')$ is used to check whether a vertex is blocked in a sample.

>>>>

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        \kktodo{uzerinden 
        gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $A_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its outgoing edges\\ %%FIXME
        $\Gamma_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its incoming edges\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
        \hline\hline
        $w_{u,v}$             & Sampling probability for the edge $(u,v)$\\
        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal Gain after last sketch build\\
        $Err_l$         & Local estimation error of the sketch\\
        $Err_g$         & Global estimation error of the sketch\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c}$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

\begin{figure}[!ht] 
    \centering
  \subfloat[\small{IC}\label{fig:ic}]{%
       \includegraphics[width=0.37\linewidth]{images/ic.pdf}}
  \subfloat[\small{WC}\label{fig:wc}]{%
        \includegraphics[width=0.37\linewidth]{images/wc.pdf}}
    \\% IMAGES HERE
  \caption{\protect\subref{fig:ic} 
\kktodo{a parti nonuniform weight olsun}\ggx{done.} The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
\protect\subref{fig:wc}
The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
  }
  %\label{fig_ic_model} 
  \label{fig:xx} 
\end{figure}

@@

\item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set the edge weights as shown in Figure~\ref{fig:wc}.
The method, as described in~\cite{kempe2003maximizing}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
of incoming edges of $v$~(which in the original graph is equal to $\Gamma _G(v)$).
Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var }\ggx{fixed.} 
% Note that the model is originally defined for undirected graphs in~\cite{kempe2003maximizing}. However, the definition above is consistent since one can consider each~(undirected) edge as two directed edges.

@@

The reachability set of a vertex is the union of all its connected vertices (via outgoing edges). Many IM kernels exploit this property to some degree. The methods based on {\em reverse reachability} \cite{borgs2014maximizing} \kktodo{cite}\ggx{done.} 
%and {\em bottom-up traversal} \\kktodo{cite} \ggx{buna referans dusunmem gerekli}
utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced. {\em MixGreedy} \cite{MixGreedy} \kktodo{cite}\ggx{cited.} goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set. Therefore, all the reachability sets within a single sample subgraph can be found via a single graph traversal.

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
If one-hot vectors are used to store the reachability sets for constant insertion time, $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity. 
If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ \kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann\cite{ackermann1928hilbertschen} function. \kktodo{bu Ackermann'a atif verelim}.\ggx{done.}

@@

In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average length of the longest leading zeros. Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed by taking the pairwise maximums of their registers. Formally; 
\begin{equation}
\label{eq:sketch-merge}
    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq J.
\end{equation} 
In our implementation, the merge operations are performed if and only if there is an edge between the vertices in respective samples \kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}. \ggx{ j'th sampleda vertexler arasında sampled edge olmasını kastetmiştim. Yanlis olmus.}

@@

Most IM algorithms have the same few steps to find the best seed vertex set; sampling, building the influence oracle, verifying the impact of new candidates, and removing the latent seed set's residual reachability set. Following the idea proposed in~\cite{infuser}, \acro fuses the sampling step with other steps to avoid reading the graph multiple times.

@@

Throughout the process, each register is used only for a single sample/simulation. 
% A merge operation for an edge ($u, v$) of the graph is performed on $v$'s register if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration. 
A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.

This process iteratively relays the reachability information among the vertices. At each iteration, vertices neighbors' reachability sets are added to their sketches.
%At each iteration, the sketches of the existing reachable vertices are modified. \kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together. 
This recursive formulation of the influence allows us to estimate the marginal influence for all vertices very fast. 
After the computation of reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches. Then \acro calculates the reachability set of the latent seed set, i.e., the one that contains the current set and $v$, by performing Monte-Carlo simulations. The vertices in the reachability sets are removed from the live set, $L$.%labeled as {\em visited}. 
\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} in the respective samples. So that, in later iterations these vertices will not contribute to the marginal gain. Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate. \kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok. $u \notin R_S$ şeklinde.}

\subsection{Hash-based Fused Sampling}
The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process. If performed individually as a preprocessing step, as the literature traditionally does, the sampling stage can be expensive, furthermore, a time-wise dominating one for the overall IM kernel; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large, and second, if samples are memoized, the memory requirement can be a multiple of the graph size. 
In this work, we borrow the fused sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
\kktodo{burata alttaki figure atfen basitce ne oldugunu anlatan 2-3 cumle gerek} 
In figure \ref{fig:traversal}, we illustrate the fused sampling process; instead of processing samples independently as in \ref{fig:sims}, Fused-sampling approach process all samples for each edge as shown in \ref{fig:fused}. This allows us to process each edge only few times instead of traversing them repeatedly for all simulations.

@@

\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{./images/bias.pdf}
    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks. \kktodo{bias matematiksel olarak nasil hesaplanir. bunu buraya yazalim}}\ggx{Python scipy ile hesaplamıştım, kodunu bulamadım. Bunun için süreye ihtiyacım var. Murmur3 ü tekrar test etmemize gerek olmamalı, bunu çıkartabiliriz diye düşünüyorum. }
    \label{fig:prob-bias} 
\end{figure}

% For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
% Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. 
%Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
Being able to generate the samples on the fly allows us to avoid many memory accesses. The only downside of hash-based fused sampling is that we have to generate all these random values,   $P(u,v)_r$, for each edge traversal and each simulation $r$. The edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage the performance gains of fused sampling better. Fortunately, the rest of the operations, i.e., one XOR and one division, are very fast on modern computing hardware. %The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.

@@

\begin{algorithm}
\caption{\sc{\acro}($G,K,J$)}
\label{algo:main}
\algorithmicrequire{$G = (V,E)$: the influence graph
\\\hspace*{6.6ex}{$K$: number of seed vertices
\\\hspace*{6.7ex}$J$: number of MC simulations}\\}
\algorithmicensure{$S$: a seed set that maximizes influence on $G$
}
\begin{algorithmic}[1]
    \State {$S \leftarrow \{\emptyset\}$}
    \For{$ v\in V$} {\bf in parallel}
        \For{$ j\in J$}
            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
        \EndFor
    \EndFor
    \State $M \leftarrow ${\sc Simulate}$(G,M,\emptyset)$
    \State $M_{S'} \leftarrow zeros(J)$
    \State $\varsigma \leftarrow 0$
    \For{$k=1\ldots K$}
        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}}\{${\sc Estimate}$(${\sc Merge}$(M_{S'},M_v))$\}\kktodo{S' nedir}\ggx{ latent seed set after rebuild}
        \State $S \leftarrow S \cup \{s\}$
        \State $e \leftarrow ${\sc Estimate}$(${\sc Merge}$(M_{S'},M_s))$
        % \State $R_S \leftarrow run\_cascade(G,S,J)$
        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ \kktodo{buna da bir algoritma eklesek} }\ggx{Yayın konusu dışında kalabilir diye çıkartmıştık.}
        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
        \State $\delta = \sigma - \varsigma$
        \State $Err_l=|(e - \delta) / \delta|$
        \State $Err_g=|e-\delta| / \sigma $
        \If{$ Err_l < \epsilon_l \lor Err_g < \epsilon_g$} %FIXME
            \State $M_{S'} \leftarrow merge(M_{S'},M_s)$
        \Else
            \For{$ v\in V$} {\bf in parallel}
                \For{$ j\in J$}
                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
                \EndFor
            \EndFor
            \State $M \leftarrow ${\sc Simulate}$(G,M,R_{S})$
            \State $M_{S'} \leftarrow zeros(J) $ 
            \State $\varsigma \leftarrow \sigma $ 
        \EndIf
    \EndFor
    \State \Return $S$
\end{algorithmic}
\end{algorithm}

 Algorithm~\ref{algo:main} first initializes the reachability sets of all vertices by adding the vertices themselves. 
 That is for all vertices $u$, its $j$th register is set to $M_u[j]=clz(h_j(u))$ meaning $R_{{G}_j}(u) = \{u\}$ where $G_j$ is the $j$th sampled graph. 
 Then, we perform the diffusion process on the sketch registers. 
 To initiate the process, all the vertices are added to the {\em live vertex set} $L$. 
 Then the incoming edges of the live vertices are processed. 
 For all vertices, $u$, its sketch, $M_u$, is updated by merging sketchs $M_v$ of all neighbors vertices $v \in {L}$. Merge result $M[j] = max(M_u[j],M_v[j])$ is written back to $M_u[j]$. This approach can be seen as a bottom-up diffusion process on underlying data-structure. At each iteration, one level of cardinality information is pulled from vertices neighbors to vertices itself.

%  If a vertex $u$ is live, its outgoing edges $(u, v)$ s.t. $v \in \Gamma_G(v)$ are processed and the sketches of $v$ are merged into those of $u$. \kktodo{burada edgeleri tersten process ettigimizi aciklamamiz gerek} burasi yanlis

 If any of $u$'s sketch registers change, it is added to the live vertex set $L'$ of the next iteration. After the incoming edges of all live vertices are processed, the current iteration ends. If the cardinality of the next iteration's live vertex set, $|L'|$, is smaller than the convergence threshold $\epsilon_c$, the diffusion stops. Otherwise, $L$ is set to $L'$, and $L'$ is cleared. Then, the next iteration starts. Figure~\ref{fig:hf-processing} shows how \acro performs two simulations at the same time using sketch registers.

\begin{figure*}[!ht]
    \begin{center}
    \includegraphics[width=0.7\linewidth]{images/sketch-diffusion.pdf}
    \caption{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green), and their registers are initialized with the length of the zero prefix of their hashes. (b) 
    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
    For the live edge between Vertex 1 and 4, \kktodo{bu edge nedir - outgoing luyor?} the register is set to the maximum of the respective register. Since the first register of vertex 1 has a larger value, we only update the second register. Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register. Notice that we are moving registers in reverse, from target to source of the edges. We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.  (d) All vertices have registers converged. There are no live vertices. }\label{fig:hf-processing} 
    \end{center}
    \end{figure*}

@@

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.8\linewidth]{images/sketch-saturation.pdf}
    \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding. \kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel} \ggx{Bunun için süreye ihtiyacım var. Diğer algorithmlar mavi çizgi gibi olmalı,(SKIM hariç) }
     }\label{fig:sketch-saturation} 
    \end{center}
\end{figure}

@@

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors. \acro allows us to work on smaller problem after each rebuilding. We remove influenced vertices from their respective samples and reachability sets are computed on this subgraph. Therefore, we only need to consider {\em latent} seed vertices, $S'$, that are chosen after the sketch rebuild.

After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The estimation error is calculated as the following; we store influence score after each sketch rebuild on $\varsigma$ and sketch cardinality estimate of the candidate vertex on $e$. We calculate the marginal gain after the last sketch build, $\delta=\varsigma - \sigma$. Then, the local estimation error will be $Err_l=|(e-\delta) / \delta|$ \kktodo{deltayi deltaya niye boluyoruz, ne cikmasini bekliyoruz}\ggx{c/p parantezi silmis, parantez ekledim.} and global error rate $Err_g=|(e-\delta) / \sigma|$. 
The sketches are assumed as stale if the absolute error in the estimated total influence score, $Err_g$, is more than the global threshold, $\epsilon_{g}$, 
and the marginal gain estimation error, $Err_l$, after the last sketch is larger than a local threshold $\epsilon_{l}$.

Before rebuilding stale sketches, the reachability set of the latent seed set, $R_G(S')$, is marked as visited and considered blocked in their respective simulations while rebuilding the sketches. Then, the sketches are rebuilt using Monte-Carlo simulations. After rebuilding, $M_{S'}$, which holds the seed vertices' cardinality estimate added after the last rebuild, is cleared with all zeros.
